Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-10-06 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:10:06	19:32:19	(Tue 6.Oct)

In this work we apply the LCA method to data from the Kongsberg Maritime HISAS 1030 synthetic aperture sonar (SAS). It has 32 sensors, operates at 100\,kHz and an opening angle of 25$^\circ$. We focus on using LCA with variations of the parametric Kaiser window, but a comparison to using trigonometric windows will also be provided. Unlike Synnev\aa{}g we steer all our windows and not just some, and elaborate on the type of Kaiser windows to include and the method of steering.

We will show that when a robust MVDR is applied to experimental data, the weights it computes has responses that tend to be symmetric and steered within a fraction of the -3dB resolution of the respective window. When letting LCA choose from Kaiser windows with similar responses, we obtain images with improved noise suppression and resolution. The resolution gain is made predictable by limiting the maximum steering to a fraction of the window's -3\,dB width. Overall, LCA produces images that are similar to MVDR, but with a resolution in between that of DAS and MVDR. LCA is also inherently robust, easy to implement and fairly easy to understand.

This article is outlined as follows: In Section \ref{sec:beamforming} we offer a gentle introduction to beamforming. Then we move on to adaptive beamforming and describe the MVDR and LCA methods \ref{sec:mvdr} and \ref{sec:lca}, respectively. We use LCA with the Kaiser window which we describe in \ref{sec:lca_kaiser_windows}, and explain how we steer it in \ref{sec:lca_steering}, and by how much in \ref{sec:lca_steering_bounds}. Finally we add some remarks on using the trigonometric window instead of Kaiser in \ref{sec:lca_trigonometric}, and of of sampling considerations in \ref{sec:lca_oversampling}. Results and discussion a provided in Section \ref{sec:results_discussion}, where we study MVDR's windows to find suitable LCA ones in \ref{sec:results_lca_window_function}, assess the range of window types and steering in \ref{sec:results_window_parameters}, determine the number of windows needed in \ref{sec:results_database_size}, and add a note on computational complexity in \ref{sec:results_complexity}. A conclusion is provided in \ref{sec:conclusion}.

>>>>

We use LCA with variations of the Kaiser window, but a comparison to using trigonometric windows will also be provided. We extend Synnev\aa{}g's work by steering all our windows and not just some, and elaborate on the type of Kaiser windows to include and the method of steering. Then the method is applied to experimental data from the 32 element Kongsberg Maritime HISAS 1030 synthetic aperture sonar (SAS), with an operating frequency of 100\,kHz and transmit angle of 25$^\circ$.

Our results show that MVDR computes weights with responses that tend to be symmetric and steered within a fraction of the window's -\,3dB resolution. When letting LCA choose from Kaiser windows with similar responses, we obtain images with improved noise suppression and resolution. The resolution gain is made predictable by limiting the maximum steering to a fraction of the window's -3\,dB width. Overall, LCA produces images that are similar to MVDR, but with a resolution in between that of DAS and MVDR. LCA is also inherently robust, easy to implement and fairly easy to understand.

This article is outlined as follows: In Section \ref{sec:beamforming} we offer a gentle introduction to beamforming. Then we move on to adaptive beamforming and describe the MVDR and LCA methods \ref{sec:mvdr} and \ref{sec:lca}, respectively. We use LCA with the Kaiser window which we describe in \ref{sec:lca_kaiser_windows}, explain how we steer it in \ref{sec:lca_steering}, and by how much in \ref{sec:lca_steering_bounds}. Finally we add some remarks on using the trigonometric window instead of Kaiser in \ref{sec:lca_trigonometric}, and of of sampling considerations in \ref{sec:lca_oversampling}. Results and discussion a provided in Section \ref{sec:results_discussion}, where we study MVDR's windows to find suitable LCA ones in \ref{sec:results_lca_window_function}, assess the range of window types and steering in \ref{sec:results_window_parameters}, determine the number of windows needed in \ref{sec:results_database_size}, and add a note on computational complexity in \ref{sec:results_complexity}. Finally we conclude in \ref{sec:conclusion}.
